### 2014-08-31 Paper_v1.tex
Updated captions for Fig 7 - 8

% Begin ...
\begin{document}
\begin{titlepage}
{\par\centering\textbf{\Large Dynamic Modeling of Biochemical Networks using Effective Kinetic Models}}
\vspace{0.05in}
{\par \centering \large{Joseph A. Wayman, Adithya Sagar and Jeffrey D. Varner$^{*}$}}
\vspace{0.10in}
{\par \centering \large{School of Chemical and Biomolecular Engineering}}
{\par \centering \large{Cornell University, Ithaca NY 14853}}
\vspace{0.1in}
{\par \centering \textbf{Running Title:}~Effective models of metabolism}
\vspace{0.1in}
{\par \centering \textbf{To be submitted:}~\emph{Processes}}
\vspace{0.5in}
{\par \centering $^{*}$Corresponding author:}
{\par \centering Jeffrey D. Varner,}
{\par \centering Associate Professor, School of Chemical and Biomolecular Engineering,}
{\par \centering 244 Olin Hall, Cornell University, Ithaca NY, 14853} 
{\par \centering Email: jdv27@cornell.edu} 
{\par \centering Phone: (607) 255 - 4258}
{\par \centering Fax: (607) 255 - 9166}
\end{titlepage}
\date{}
\thispagestyle{empty}
\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Abstract}

@@

\section*{Introduction}
Biochemical processes are widely used in biotechnology to produce an array of products including commodity chemicals and protein therapeutics.
However, whole-cell processes share the central limitation of requiring cell growth, 
which redirects resources away from product synthesis, and cell walls, which complicate interrogation and control of intracellular metabolic processes.
On the other hand, cell-free metabolic systems offer many advantages over traditional in vivo production methods. 
For example, cell-free systems can direct scarce metabolic resources exclusively towards a single product of interest. 
Moreover, with no cell wall, cell free systems can more easily be interrogated, and substrates of the metabolite processes directly controlled.
Cell free production offers the unique opportunity to study metabolism without the complication of cell growth and gene expression processes.
For modeling, this implies that we need only consider allosteric regulation of enzyme activity when building and testing cell free metabolic models.
Of course, modeling allosteric mechanisms is itself a difficult problem when the model is at a whole genome scale. To address this problem, we have developed a
an approach based upon the constrained fuzzy logic framework of Morris and Lauffenburger [REFHERE].

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{./figs/Figure-7-ControlSearch.pdf}
\caption{Combined control structure and kinetic parameter search results. Think about this ...}\label{fig-control-search}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1.0\textwidth,height=0.6\textheight]{./figs/Figure-8-Flux.pdf}
\caption{Flux and control pattern for estimated model parameters and structures. }\label{fig-flux-pattern}
\end{figure}

>>>>

% Begin ...
\begin{document}
\begin{titlepage}
{\par\centering\textbf{\Large Dynamic Modeling of Cell-Free Biochemical Networks using Effective Kinetic Models}}
\vspace{0.05in}
{\par \centering \large{Joseph A. Wayman, Adithya Sagar and Jeffrey D. Varner$^{*}$}}
\vspace{0.10in}
{\par \centering \large{School of Chemical and Biomolecular Engineering}}
{\par \centering \large{Cornell University, Ithaca NY 14853}}
\vspace{0.1in}
{\par \centering \textbf{Running Title:}~Effective models of metabolism}
\vspace{0.1in}
{\par \centering \textbf{To be submitted:}~\emph{Processes}}
\vspace{0.5in}
{\par \centering $^{*}$Corresponding author:}
{\par \centering Jeffrey D. Varner,}
{\par \centering Associate Professor, School of Chemical and Biomolecular Engineering,}
{\par \centering 244 Olin Hall, Cornell University, Ithaca NY, 14853} 
{\par \centering Email: jdv27@cornell.edu} 
{\par \centering Phone: (607) 255 - 4258}
{\par \centering Fax: (607) 255 - 9166}
\end{titlepage}
\date{}
\thispagestyle{empty}
\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Abstract}

@@

\section*{Introduction}
Biological processes are widely used in industrially to produce an array of products from commodity chemicals and to high-value protein therapeutics.
However, whole-cell processes share the central limitation of requiring cell growth, 
which redirects resources away from product synthesis, and cell walls, which complicate interrogation and control of intracellular metabolic processes.
On the other hand, cell-free metabolic systems offer many advantages over traditional in vivo production methods. 
For example, cell-free systems can direct scarce metabolic resources exclusively towards a single product of interest. 
Moreover, with no cell wall, cell free systems can more easily be interrogated, and substrates of the metabolite processes directly controlled.
Cell free production offers the unique opportunity to study metabolism without the complication of cell growth and gene expression processes.
For modeling, this implies that we need only consider allosteric regulation of enzyme activity when building and testing cell free metabolic models.
Of course, modeling allosteric mechanisms is itself a difficult problem when the model is at a whole genome scale. To address this problem, we have developed a
an approach based upon the constrained fuzzy logic framework of Morris and Lauffenburger [REFHERE].

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{./figs/Figure-7-ControlSearch.pdf}
\caption{Combined control and kinetic parameter search using modified particle swarm optimization (PSO). 
A population of N = 100 particles was initialized with randomized kinetic parameters and one of five possible control configurations (Network A - E).
Simulation error was minimized for a synthetic data set 
($S$, end-product P$_{1}$ and intermediate M$_5$ sampled approximately every 20 min) generated using Network A.
\textbf{A}: Simulation error versus parameter set angle for N = 100 particles biased toward the correct regulatory program (A,B,C,D,E) = (40\%, 30\%, 10\%,10\% and 10\%).
\textbf{B}: Simulation error versus parameter set angle for N = 100 uniformly distributed particles (A,B,C,D,E) = (20\%, 20\%, 20\%, 20\% and 20\%).
\textbf{C}: Simulation error versus parameter set angle for N = 100 negatively biased particles (A,B,C,D,E) = (10\%, 10\%, 10\%, 30\% and 40\%).
Network A (the correct structure) was preferentially identified for positively and uniform biased particle distributions, but misidentified in the presence of
a large incorrect bias. 
}\label{fig-control-search}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1.0\textwidth,height=0.6\textheight]{./figs/Figure-8-Flux.pdf}
\caption{Metabolic flux and control program output as a function of network type and parameter estimate.
The population of particles from the modified particle swarm optimization strategy were sorted based upon simulation error. 
The scaled metabolic flux and control variables governing the activity of $E_{1},E_{3}$ and $E_{6}$ were plotted for each particle in the swarm.
\textbf{A}: Model performance for the N = 100 positively biased particles.
\textbf{B}: Model performance for the N = 100 uniformly biased particles.
\textbf{C}: Model performance for the N = 100 negatively biased particles.
}\label{fig-flux-pattern}
\end{figure}
